### 2015-09-17 plosOne/plos.tex
adicionado arquivo com cabecalho correto

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Social Participation Ontology: community documentation, enhancements and use examples}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Renato Fabbri\textsuperscript{1},
Henrique Parra Parra Filho\textsuperscript{2},
Rodrigo Bandeira de Luna\textsuperscript{2},
Ricardo Augusto Poppi Martins\textsuperscript{3},
Flor Karina Mamani Amanqui\textsuperscript{4},
Dilvan de Abreu Moreira\textsuperscript{4}
%\textsuperscript{3,*},
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
%\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\bf{1} S\~ao Carlos Institute of Physics, University of S\~ao Paulo, CP 369, 13560-970, S\~ao Carlos, SP, Brazil, \url{fabbri@usp.br}
\\
\bf{2} Cidade Democr\'atica, Instituto Seva, S\~ao Paulo, SP, Brazil
\\
\bf{3} National Secretariat of Social Participation, General Secretariat of the Republic, Bras\'ilia, Federal District, Brazil
\\
\bf{4}  Institute of Mathematical and Computer Sciences, University of São Paulo, S\~ao Carlos, SP, Brazil
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
%\textcurrency S\~ao Carlos Institute of Physics, University of S\~ao Paulo, CP 369, 13560-970 S\~ao Carlos, SP, Brazil
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased
%
%% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.
%
% Use the asterisk to denote corresponding authorship and provide email address in note below.
%* CorrespondingAuthor@institute.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{equation}\label{eq:schemeP} 
D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
\end{equation}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

% For figure citations, please use "Fig." instead of "Figure".
Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{figure}[h]
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\begin{enumerate}
\item{react}
\item{diffuse free particles}
\item{increment time by dt and go to 1}
\end{enumerate}

% Results and Discussion can be combined.
\section*{Results}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

\subsection*{Sed ac quam id nisi malesuada congue.}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}. 
\subsection*{Subsection 1}
Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{Subsection 2}
\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Text}.

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
\subsection*{S1 Video}
\label{S1_Video}
{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Text}
\label{S1_Text}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Fig}
\label{S1_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S2 Fig}
\label{S2_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Table}
\label{S1_Table}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{bib1}
Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005

\bibitem{bib2}
Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.

\end{thebibliography}

\end{document}

### 2015-09-17 plosOne/SI/S1glossary.tex
adicionada primeiro arquivo do supporting information

\documentclass{article}
\newcommand{\ops}{\textsc{ops}}
\newcommand{\opsi}{O\textsc{ps}}
\newcommand{\vcps}{\textsc{vcps}}
\newcommand{\owl}{\textsc{owl}}
\newcommand{\owli}{O\textsc{wl}}
\newcommand{\sparql}{\textsc{s}par\textsc{ql}}
\newcommand{\bfo}{\textsc{bfo}}
\newcommand{\dbpedia}{\textsc{db}pedia}
\newcommand{\foaf}{\textsc{foaf}}
\newcommand{\ict}{\textsc{ict}}
\newcommand{\html}{\textsc{html}}
\newcommand{\node}{\textsc{n}ode.js}
\newcommand{\facebook}{\textsc{f}acebook}
\newcommand{\twitter}{\textsc{t}witter}
\newcommand{\wwwc}{\textsc{w3c}}
\newcommand{\skos}{\textsc{skos}}
\newcommand{\etherpad}{\textsc{e}therpad}
\newcommand{\ogp}{\textsc{ogp}}
\newcommand{\iri}{\textsc{iri}}
\newcommand{\uri}{\textsc{uri}}
\newcommand{\urii}{U\textsc{ri}}
\newcommand{\urll}{\textsc{url}}
\newcommand{\ngo}{\textsc{ngo}}
\newcommand{\http}{\textsc{http}}
\newcommand{\opa}{\textsc{op}a}
\newcommand{\ocd}{\textsc{ocd}}
\newcommand{\ontologiaa}{\textsc{o}ntologiaa}
\newcommand{\obs}{\textsc{obs}}
\newcommand{\pubby}{\textsc{p}ubby}
\newcommand{\rdf}{\textsc{rdf}}
\newcommand{\mysql}{\textsc{m}y\textsc{sql}}
\newcommand{\aan}{\textsc{aa}}
\newcommand{\cidadedemocratica}{\textsc{c}idade \textsc{d}emocr\'atica}
\newcommand{\participa}{\textsc{p}articipa.br}
\newcommand{\ontop}{\textsc{o}n\textsc{t}op}
\newcommand{\quest}{\textsc{q}uest}
\newcommand{\webprotege}{\textsc{w}ebprotege}
\newcommand{\obda}{\textsc{obda}}
\newcommand{\pnud}{\textsc{undp}}
\newcommand{\onu}{\textsc{un}}
\newcommand{\vbs}{\textsc{vbs}}
\newcommand{\lod}{\textsc{lod}}
\newcommand{\corais}{\textsc{c}orais}
\newcommand{\serpro}{\textsc{s}erpro}
\newcommand{\python}{\textsc{p}ython}
\newcommand{\protege}{\textsc{p}rot\`eg\`e}

\usepackage[margin=1em]{geometry}
\begin{document}
%\section{Glossary of terms, acronyms and abbreviations}\label{ap:glossary}
\vspace{-8cm}
The subjects involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should help readers as a concise references.
\begin{table}[!h]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
  \footnotesize
  \vspace{-6mm}
  \centering
  \caption{Glossary for current article}
  \begin{tabular}{||l|p{5cm}|p{9cm}||}\hline
      {\bf term} & {\bf meaning} & {\bf further information} \\\hline\hline
      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and proving dedication \\\hline
      \bfo  & Basic Formal Ontology & an upper ontology supporting information retrieval, analysis and integration in scientific and other domains \\\hline
      \cidadedemocratica  & a Brazilian civil society participatory portal & -//- \\\hline
      \dbpedia  & DBpedia is a crowd-sourced community effort to extract structured information from Wikipedia & consists of an ontological organization and data \\\hline
      \etherpad  & a web-based collaborative real-time editor, allowing authors to simultaneously edit a text document & -//- \\\hline
      \facebook & an online social networking service & -//-  \\\hline
      \foaf  & Friend Of A Friend & an ontology devoted to linking people and information using the Web, \foaf\ is a core ontology of the web semantic/linked data academic community \\\hline
      \html  & HyperText Markup Language & the standard markup language used to create Web pages \\\hline
      \http  & Hypertext Transfer Protocol & an application protocol for distributed, collaborative, hypermedia information systems. It is the foundation of data communication for the World Wide Web \\\hline
      \ict  & Information and communications technology  & often used as an extended synonym for information technology (IT) \\\hline
      \iri  & Internationalized Resource Identifier & a new internet standard to extend upon the existing uniform resource identifier (\uri) scheme, where \iri s are always utf-8 \\\hline
      \lod  & Linked Open Data & a human legacy of open and linked data \\\hline
      \mysql  & a widely used open-source relational database management system & -//-\\\hline
      \ngo  & Non-Governmental Organization & a term commonly used for an organization that is neither a part of a government nor a conventional for-profit business \\\hline
      \node  & an open source, cross-platform runtime environment for server-side and networking applications & applications are written in JavaScript  \\\hline
      \obda  & Ontology-Based Database Access & a general term for accessing databases through ontological criteria \\\hline
      \obs  & Social Library Ontology & from the Brazilian name Ontologia da Biblioteca Social \\\hline
      \ocd  & Cidade Democr\'atica Ontology & from the Brazilian name Ontologia do Cidade Democr\'atica \\\hline
      \ogp  & Open Government Partnership & an international organization promoting multilateral initiative and seeking strong commitments from participating government institutions to promote transparency, increase civic participation, fight corruption, and harness new technologies to make government more open, effective, and accountable \\\hline
      \ontologiaa  & \aan\ Ontology. &  the name is a derivative from the Brazilian ``Ontologia do \aan''. It is small, simple and entirely linked to upper ontologies (classes and properties) \\ \hline
      \ontop  & a platform to query databases as virtual \rdf\ graphs using \sparql\ & -//- \\\hline
      \opa  & \participa\ Ontology & from the Brazilian name Ontologia do \participa \\\hline
      \ops  & Ontology of Social Participation & Acronym from the Brazilian name: Ontologia de Participa\c{c}\~ao Social \\\hline
      \owl  & Web Ontology Language & for authoring ontologies \\\hline
      \participa  & the Brazilian federal participatory portal & -//- \\\hline
      \pubby  & A Linked Data Front-end for dereferencing \uri s & -//- \\\hline
      \python  & a widely used general-purpose, high-level programming language & known as an easy scripting language among researchers, developers and hackers \\\hline
      \quest  & the \sparql\ engine/reasoner that comes with \ontop & -//- \\\hline
      \rdf  & Resource Description Framework & a standard model for data interchange on the Web \\\hline
      \serpro  & Brazilian Federal Service of Data Processing & the biggest government-owned corporation of IT services of Brazil \\\hline
      \skos  & Simple Knowledge Organization System & a \wwwc recommendation designed for representation of thesauri, classification schemes, taxonomies, subject-heading systems \\\hline
      \sparql  & \sparql\ Protocol and \rdf\ Query Language & an \rdf\ query language  \\\hline
      \onu  & United Nations & an intergovernmental organization to promote international co-operation \\\hline
      \pnud  & United Nations Development Programme & the United Nations' global development network \\\hline
      \urll  & Uniform Resource Locator & also known as a web address, particularly when used with \http \\\hline
      \vbs  & Social Library Vocabulary & from the Brazilian name Vocabulário da Biblioteca Social \\\hline
      \vcps  & Common Vocabulary of Social Participation & Acronym from the Brazilian Vocabul\'ario Comum de Participa\c{c}\~ao Social\\\hline
      \wwwc     & World Wide Web Consortium & the main international standards organization for the World Wide Web \\\hline
\end{tabular}
  \label{tab:glos}
%\end{adjustwidth}
\end{table}

\end{document}

### 2015-09-20 plosOne/cover/coverLetter.tex
added initial cover letter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Lined Cover Letter
% LaTeX Template
% Version 1.0 (1/6/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Matthew J. Miller
% http://www.matthewjmiller.net/howtos/customized-cover-letter-scripts/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,stdletter,dateno,sigleft]{newlfm} % Extra options: 'sigleft' for a left-aligned signature, 'stdletternofrom' to remove the from address, 'letterpaper' for US letter paper - consult the newlfm class manual for more options

\usepackage{charter} % Use the Charter font for the document text

\newsavebox{\Luiuc}\sbox{\Luiuc}{\parbox[b]{1.75in}{\vspace{0.5in}
\includegraphics[width=1.\linewidth]{USP.jpg}}} % Company/institution logo at the top left of the page
\makeletterhead{Uiuc}{\Lheader{\usebox{\Luiuc}}}

\newlfmP{sigsize=50pt} % Slightly decrease the height of the signature field
\newlfmP{addrfromphone} % Print a phone number under the sender's address
\newlfmP{addrfromemail} % Print an email address under the sender's address
\PhrPhone{Phone} % Customize the "Telephone" text
\PhrEmail{Email} % Customize the "E-mail" text

\lthUiuc % Print the company/institution logo

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\namefrom{Renato Fabbri} % Name

\addrfrom{
\today\\[12pt] % Date
%123 Broadway \\ % Address
%City, State 12345
University of S\~ao Paulo,\\
CP 369, 13560-970,\\
S\~ao Carlos, SP, Brazil
}

\phonefrom{+55 (16) 98107 7222} % Phone number

\emailfrom{fabbri@usp.br} % Email address

%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING/CLOSING
%----------------------------------------------------------------------------------------

\greetto{Dear PLOS ONE Editors,} % Greeting text
\closeline{Thank you for your consideration! \newline \newline Sincerely yours,} % Closing text

\nameto{}%PLOS ONE Editors} % Addressee of the letter above the to address

\addrto{
%PLOS Offices % To address
}

%----------------------------------------------------------------------------------------

\begin{document}
\begin{newlfm}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

	Please find attached the manuscript entitled "Social Participation Ontology: community documentation, enhancements and use examples", which we submit for publication in the PLOS ONE Journal. The reasons why we chose PLOS ONE as the vehicle for our manuscript are as follows.
	In the manuscript we report the development of a participatory upper OWL ontolgy.
	We were unable to find similar conceptualization in literature, although consistent with other upper ontologies and characterizations of such social structures.
	The ontologic structures have had some uses in linked data sharing and conceptual maturing.
	Handpicked examples are the use by the Brazilian social participation portal for sharing linked data
	and the international process of first conceptualizations.
	This document have been used as a reference by community but lacks a peer review chancel.
	All data, scripts and documentation are open since first versions, including the submited article.
	Processes are also kept open, with traces in git repositories, data repositories,
	dedicated portals, and specialized gadgets.
	Because the methods and results are multidisciplinary, compliant with open information standards and with aplications of public interest,
	we take the view that the manuscript may be of interest to a very wide readership.
	 We believe that NJP is therefore the ideal vehicle for this type of scientific contribution.
	 If
	 you feel that the manuscript is appropriate for your journal, we suggest the following reviewers: 
	 Tudor Groza,
	 Indra Neil Sarkar,                                                        and 
	 Chris Mavergames.

%In addition to demonstrating the temporal stability and benchmarking, these results enable sound observation of both network and participant outliers and the consideration of the textual production of the networks, sectors and participants. Therefore, the document also presents a first consideration of typologies in such context, which bridges exact and human sciences. Indeed, the authors of the manuscript belong to different fields, and the principles adopted in the research comply with open science principles, as the email data are officially part of the GMANE database, scripts are official PyPI packages, data from other social networks and further scripts are in public Git repository. Furthermore, all the details of the theoretical developments and the results generated are given in a supplementary Supporting Information file, which will serve as guidance for anyone  interested in the field.
%	Because the methods applied belong to the realms of statistical physics (mainly) and since the subject is absolutely generic, we take the view that the manuscript may be of interest to a very wide readership. We believe that NJP is therefore the ideal vehicle for this type of scientific contribution.
%
%PARAGRAPH ONE: State the reason for the letter, name the position or type of work you are applying for and identify the source from which you learned of the opening (i.e. career development center, newspaper, employment service, personal contact).
%
%PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products, services - above all, stress what you can do for the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate for the position. If you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the same information the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your qualifications, training, and experiences. The purpose of this section is to strengthen your resume by providing details which bring your experiences to life. 
% 
%PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview. Alternatively, state that you will call on a certain date to set up an interview. End the letter by thanking the employer for taking time to consider your credentials.

%----------------------------------------------------------------------------------------

\end{newlfm}
\end{document}

### 2015-09-20 plosOne/cover/coverLetter.tex
terminada formatacao da cover letter
reviewed cover letter

@@
 
-\namefrom{Renato Fabbri} % Name
+\namefrom{\includegraphics[width=0.2\textwidth]{assinatura-2011-07-06__}\newline\newline Renato Fabbri} % Name
 
@@
 The reasons why we chose PLOS ONE as the vehicle for our manuscript are as follows.
-	In the manuscript we report the development of a participatory upper OWL ontolgy.
+	In the manuscript we report the development of a participatory upper OWL ontology.
 	We were unable to find similar conceptualization in literature, although consistent with other upper ontologies and characterizations of such social structures.
 	The ontologic structures have had some uses in linked data sharing and conceptual maturing.
-	Handpicked examples are the use by the Brazilian social participation portal for sharing linked data
+	Handpicked examples are the use by the Brazilian federal social participation portal for sharing linked data
 	and the international process of first conceptualizations.
-	This document have been used as a reference by community but lacks a peer review chancel.
-	All data, scripts and documentation are open since first versions, including the submited article.
+	This research article have been used as a reference by community but lacks a peer review chancel.
+	All data, scripts and documentation are open since first versions, including the submitted article.
 	Processes are also kept open, with traces in git repositories, data repositories,
 	dedicated portals, and specialized gadgets.
-	Because the methods and results are multidisciplinary, compliant with open information standards and with aplications of public interest,
+	Because the methods and results are multidisciplinary, compliant with open information standards and with applications of public interest,
 	we take the view that the manuscript may be of interest to a very wide readership.
-	 We believe that NJP is therefore the ideal vehicle for this type of scientific contribution.
+	 We believe that PLOS ONE is therefore the ideal vehicle for this type of scientific contribution.
 	 If
@@
 	 Chris Mavergames.
+
+%
+%	 \begin{figure}[!h]
+%%		         \includegraphics[width=0.1\textwidth]{assinatura-2011-07-06_}
+%		 \centering
+%		         \includegraphics[width=0.1\textwidth]{assinatura-2011-07-06_}
+%		 \end{figure}
+%
 
@@
 %----------------------------------------------------------------------------------------
-
 \end{newlfm}

### 2015-09-22 plosOne/SI/S1glossary.tex
revisados SIs

@@
 
+\usepackage{nameref,hyperref}
+\usepackage{xcolor}       
+\hypersetup{
+        colorlinks,
+        linkcolor={red!50!black},
+        citecolor={blue!50!black},
+        urlcolor={blue!80!black}
+}
+
 \usepackage[margin=1em]{geometry}
@@
 \vspace{-8cm}
-The subjects involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should help readers as a concise references.
+The knowledge fields involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should assist readers as a concise reference.
 \begin{table}[!h]
@@
       {\bf term} & {\bf meaning} & {\bf further information} \\\hline\hline
-      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and proving dedication \\\hline
+      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and demonstration of dedication \\\hline
       \bfo  & Basic Formal Ontology & an upper ontology supporting information retrieval, analysis and integration in scientific and other domains \\\hline
